### 2024-07-23 modern-portfolio-theory.qmd
20240723 - diversification

>>>>

- diversify; do not put all your eggs in one basket

In terms of diversification, it can be helpful to diversify in multiple ways.
First, it can be helpful not to rely on just one or two "stud" players.
If they are on bye or have a down week, your team is more likely to suffer.
Also, there are risks in picking multiple offensive players from the same team.
For instance, if you have the Quarterback and Wide Receiver from the same team, and the team has a poor offensive outing, that will have a greater impact.
Having multiple players on a juggernaut offense can be a boon, but it can be challenging to predict which offense will lead the league.
